The \dealii{} Library, Version 8.5

### 2017-03-20 8.5/paper.tex
Add myself.

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Jean-Paul Pelteret,
    David Wells
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}

@@

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[9]{Bruno Turcksin\footnote{
  This manuscript has been authored by UT-Battelle, LLC under Contract No.
  DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
  Government retains and the publisher, by accepting the article for
  publication, acknowledges that the United States Government retains a
  non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
  the published form of this manuscript, or allow others to do so, for United
  States Government purposes. The Department of Energy will provide public
  access to these results of federally sponsored research in accordance with the
  DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
\affil[9]{Computational Engineering and Energy Sciences Group,
  Computional Sciences and Engineering Division,
  Oak Ridge National Laboratory, 1 Bethel Valley Rd., 
  TN 37831, USA
  {\texttt{turcksinbr@ornl.gov}}}

\author[10]{David Wells}
\affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}

@@

B.~Turcksin: This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract number DE-AC05-00OR22725.
